On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-08-15 Manuscript/manuscript.tex
Almost done with final changes

The rest of this paper is organized as follows. Section~\ref{sec:Data} describes 
how data was collected and begins to detail the generalized linear mixed-effect 
(GLMM) model that is further developed in Section~\ref{sec:Methods}. The 
signed-rank test that analyzes reaction times for the same athletes across
different competitions is
also described in Section~\ref{sec:Methods}.  Section~\ref{sec:Results}
 provides the results of the two analyses and ends 
by questioning the reaction time barrier.  Lastly, Section~\ref{sec:Discussion}
discusses the impact and limitations of the paper.

@@

With our small sample size, the asymptotic normal distribution may not be
reliable, so we use random permutation, which simulates the observed test 
statistic: $W^*$ given number of times to obtain the p-value of said test 
statistics. This method is available from the \texttt{clusWilcox.test()} function
with \texttt{method = `ds'} and \texttt{exact = TRUE} from R package
\texttt{clusrank} \citep{jiang2020wilcoxon}.

@@

A summary of the two effect model is shown in table~\ref{tab:Gamma_parameters}
for the pooled datasets and shows the standard error of the year
effect increases for both the men's final and men's pooled data sets when
including 2022. We choose to only look at the pooled datasets, as R displayed
warnings when creating the finals only models
\of{Is this section okay? Please let me know what I should rework}

\begin{table}
  \centering
  \caption{Summary statistics for the two effect GLMM on various data sets. SE
  is short for standard error.} 
  \begin{tabular}{c c c c c}
      \toprule
      Dataset & Batch SE & Year SE & Intercept & Residual SE \\
      \midrule
      Old Pooled & 0.060 & 0.034 & -1.865 & 0.139 \\
      All Pooled  & 0.059 & 0.041 & -1.880 & 0.014 \\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1 and 0.08
  for various data sets.}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ 0.1) & P(RxnTime $<$ 0.08) \\ 
   \midrule
   Old Pooled & $4.15\cdot10^{-3}$ & $4.67\cdot10^{-5}$ \\ 
   All Pooled & $5.15\cdot10^{-3}$ & $6.01\cdot10^{-5}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = .001) & P(RxnTime $<$ x = 0.0001) \\ 
   \midrule
   Old Pooled & $0.093$ & $0.083$ \\ 
   All Pooled & $0.091$ & $0.082$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

\of{Should I report table~\ref{tab:EffectComparison}}
\begin{table}
  \centering
  \caption{Compares the various effect models by dataset, all probabilities are
  for observing a reaction time less than 0.1 seconds. In general the model with
  the highest probability (least extreme reaction time) is the Year Effect model.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & Year Effect & Batch Effect & Both Effects \\ 
   \midrule
   Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
   All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:EffectComparison}
\end{table}

@@

\begin{table}
  \centering
  \caption{}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & $exact = True$ & $exact \neq True$ & Sample size & Clusters/Athletes \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10{-2}$ & 65 & 15 \\ 
   Nat vs Inter & $2.2\cdot10^{-16}$ & $1.0\cdot10^{-3}$ & 49 & 11 \\
   \bottomrule
  \end{tabular}
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. Nat vs Inter compares data
  from the same athletes who competed at the 2022 national-level championships
  and the 2022 World Track and Field Championships}
  \label{tab:Clusrankresults}
\end{table}

\section{Discussion}\label{sec:Discussion}

>>>>

The rest of this paper is organized as follows. Section~\ref{sec:Data} describes 
how data was collected and begins to detail the generalized linear mixed-effect 
(GLMM) model that is further developed in Section~\ref{sec:Methods}. The 
signed-rank test that analyzes reaction times for the same athletes across
different competitions is
also described in Section~\ref{sec:Methods}.  Section~\ref{sec:Results}
 provides the results of the two analyses and ends 
by questioning the reaction time barrier.  Lastly, Section~\ref{sec:concludingremark}
discusses the impact and limitations of the paper.

@@

With our small sample size, the asymptotic normal distribution may not be
reliable, so we use 1000 random permutations to simulate the observed test 
statistic: $W^*$ given number of times to obtain the p-value of said test 
statistics. This method is available from the \texttt{clusWilcox.test()} function
with \texttt{method = `ds'} and \texttt{exact = TRUE} from R package
\texttt{clusrank} \citep{jiang2020wilcoxon}.

@@

A summary of the two effect model is shown in table~\ref{tab:Gamma_parameters}
for the pooled datasets and shows the standard error of the year
effect increases for both the men's final and men's pooled data sets when
including 2022. We choose to only look at the pooled datasets, as R displayed
warnings when creating the finals only models.  The two effect model with venue
and heat effect was the best model, as proven by an ANOVA test and decrease in
AIC.  For the entire pooled dataset; the AIC for the venue effect only model was
$-1847.9$, the heat effect only model AIC was $-1894.4$ and the both effect model,
which we will present throughout this section AIC was $-1898.9$. Thus, the two
effect model is superior and will be presented throughout the rest of the paper.
\of{How specific do I need to be in this section? Will people who read this paper
run the code to see the p value or should I say it directly and how do I say it?}

\begin{table}
  \centering
  \caption{Summary statistics for the two effect GLMM on various data sets. SE
  is short for standard error.} 
  \begin{tabular}{c c c c c c}
      \toprule
      Dataset & AIC & Batch SE & Year SE & Intercept & Residual SE \\
      \midrule
      Old Pooled & 0.060 & 0.034 & $-1.865$ & 0.139 \\
      All Pooled & 0.059 & 0.041 & $-1.880$ & 0.014 \\
      \bottomrule
  \end{tabular}
  \label{tab:Gamma_parameters}
\end{table}

@@

\begin{table}
  \centering
  \caption{Probabilities of observing reaction times less than 0.1 and 0.08
  for various data sets.}
  \begin{tabular}{c c c c} 
   \toprule
   Data Set & P(R. Time $<$ 0.08) & P(R. Time $<$ 0.09) & P(R. Time $<$ 0.1)  \\ 
   \midrule
   Old Pooled & $4.67\cdot10^{-5}$ & $5.91\cdot10^{-4}$ &  $4.15\cdot10^{-3}$  \\ 
   All Pooled & $6.01\cdot10^{-5}$ & $7.39\cdot10^{-4}$ & $5.15\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_probability}
\end{table}

@@

\begin{table}
  \centering
  \caption{Suggested reaction time barriers based on probability of observing
  a time less than the barrier. \of{Not sure if this makes sense}}
  \begin{tabular}{c c c} 
   \toprule
   Data Set & P(RxnTime $<$ x = $10^{-3}$) & P(RxnTime $<$ x = $10^{-4}$) \\ 
   \midrule
   Old Pooled & $0.093$ & $0.083$ \\ 
   All Pooled & $0.091$ & $0.082$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Sim_time}
\end{table}

%\of{Should I report table~\ref{tab:EffectComparison}}
%\begin{table}
%  \centering
%  \caption{Compares the various effect models by dataset, all probabilities are
%  for observing a reaction time less than 0.1 seconds. In general the model with
%  the highest probability (least extreme reaction time) is the Year Effect model.}
%  \begin{tabular}{c c c c} 
%   \toprule
%   Data Set & Year Effect & Batch Effect & Both Effects \\ 
%   \midrule
%   Old Pooled & $5.73\cdot10^{-3}$ & $5.21\cdot10^{-3}$ & $4.15\cdot10^{-3}$ \\ 
%   All Pooled & $6.84\cdot10^{-3}$ & $6.64\cdot10^{-3}$ & $5.15\cdot10^{-3}$ \\
%   \bottomrule
%  \end{tabular}
%  \label{tab:EffectComparison}
%\end{table}

@@

\begin{table}
  \centering
  \caption{}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $2.9\cdot10^{-3}$ & $2.3\cdot10{-2}$ \\ 
   Nat vs Inter & $2.2\cdot10^{-16}$ & $1.0\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. Nat vs Inter compares data
  from the same athletes who competed at the 2022 national-level championships
  and the 2022 World Track and Field Championships.}
  \label{tab:Clusrankresults}
\end{table}

\section{Concluding Remarks}\label{sec:concludingremarks}
